Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-22 doc/paper.Rmd
type II error rates

```{r type2, fig.width=8, fig.height=5, out.width='.8\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $w_o$. For a window size of $w_o = 120$ we see a drop in type II error rate across all type I rates considered. Smaller validation sizes $w_v$ are typically associated with a smaller type II error."}
files <- dir("../data/crossvalidate-cs2/")
cvcs2 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs2/",file))
  cvcs2 <- rbind(cvcs2, tmp)
}
cvcs2$coarse <- cvcs2$coarseness
library(plotROC)
cvcs2$method <- "CS2"

@@

errorsCV %>% 
  ggplot(aes(x = wo, y = beta, colour=factor(alpha))) + 
  geom_point(aes(shape=factor(wv)), size=3.5) +
#  facet_grid(.~wo, labeller="label_both") + 
 geom_line(aes(group=alpha),  size=.7) +
  #  geom_smooth(aes(group=alpha), se=FALSE, method="loess", size=.7) +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") +
  scale_shape_discrete(expression("Size of\nvalidation window "~w[v])) +
  xlab(expression("Window size for optimization "~w[o])) +
  ylab("Type II error rate")

labels = expression(P[M1](tilde(z)>0),P[M0](tilde(z)>0))
```

@@

```{r type22, fig.height = 3.5, fig.width = 5, out.width='0.7\\textwidth', fig.cap="ROC curves of methods CS1 and CS2 for different sizes of optimization window $w_o$. Optimal ROC curves are reached at optimization windows of size 150 and higher. Points of equal error rates (EERs) can be found at the intersection of the dotted line and the ROC curves."}

cvcs2 %>% 
  ggplot(aes(d = as.numeric(!match), m = p_value, colour=factor(wo))) + 
  geom_roc(labels=FALSE, n.cuts=100, pointsize=0) +
  geom_abline(linetype=3, slope=-1, intercept = 1, colour="grey30", size=.5) +
  theme_bw() + 
  scale_colour_brewer(
    expression("Optimization\nwindow size"~w[o]), palette="Set2") +
  facet_grid(.~method, labeller="label_both") +
  xlab("False Positives Rate (1 - Specificity)") +
  ylab("True Positives Rate (Sensitivity)")

>>>>

```{r type2, fig.height = 3, fig.width = 4.5, out.width='0.6\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $w_o$. For a window size of $w_o = 130$ we see a minimum in type II error rate across all type I rates considered. Smaller validation sizes $w_v$ are typically associated with a smaller type II error."}
files <- dir("../data/crossvalidate-cs2/")
cvcs2 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs2/",file))
  cvcs2 <- rbind(cvcs2, tmp)
}
cvcs2$coarse <- cvcs2$coarseness
library(plotROC)
cvcs2$method <- "CS2"

@@

errorsCV %>% 
  ggplot(aes(x = wo, y = beta, colour=factor(alpha))) + 
  geom_point(aes(shape=factor(wv)), size=2.5) +
  geom_line(aes(group=alpha),  size=.7) +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha),
                      palette="Set2") +
  scale_shape_discrete(expression("Size of\nvalidation window "~w[v])) +
  xlab(expression("Window size for optimization "~w[o])) +
  ylab("Type II error rate")

@@

```{r type22, fig.height = 3, fig.width = 4.5, out.width='0.6\\textwidth', fig.cap="ROC curves of methods CS1 and CS2 for different sizes of optimization window $w_o$. Optimal ROC curves are reached at optimization windows of size 150 and higher. Points of equal error rates (EERs) can be found at the intersection of the dotted line and the ROC curves."}

cvcs2 %>% 
  ggplot(aes(d = as.numeric(!match), m = p_value, colour=factor(wo))) + 
  geom_roc(labels=FALSE, n.cuts=100, pointsize=0, size=0.6) +
  geom_abline(
    linetype=3, slope=-1, intercept = 1, colour="grey30", size=.3) +
  theme_bw() + 
  scale_colour_brewer(
    expression("Optimization\nwindow size"~w[o]), palette="Set2") +
  facet_grid(.~method, labeller="label_both") +
  xlab("False Positives Rate (1 - Specificity)") +
  ylab("True Positives Rate (Sensitivity)")
